Inferring Invariants of Distributed Programs

### 2015-03-04 Doc/approach.tex
execution flow added

So we are planning to do a dynamic dataflow analysis which consists of follwing steps:
\begin{itemize}
\item Instrumenting variable declarations and assignments at the run time
\item Collecting execution traces of each of these statements by runnning test suites
\item Doing a forward flow analysis using the collected traces
\end{itemize}

@@

@@

>>>>

So we are planning to do a dynamic dataflow analysis which consists of following steps:
\begin{itemize}
\item Instrumenting variable declarations and assignments at the run time
\item Collecting execution traces of each of these statements by runnning test suites
\item Doing a forward flow analysis using the collected traces
\end{itemize}

@@

Overall execution flow of the analysis is illustrated in Figure~\ref{fig:go_flow} and works as follows:
\begin{itemize}
\item Developer annotates interesting program points in the Go program which will be used as states for mining invariants.
\item Program is instrumented to 
\begin{itemize}
\item dump variable values at the annotated program points at run time
\item wrap all RPC communication to include vector clocks
\item log all declarations and assignments for doing the forward flow analysis
\end{itemize}
 For this we are hoping to use static analysis libraries
available under Go-lang Parse package and tools\cite{static_golang} which provide
support for Identifier resolution, Type information, Call graph
navigation and Channel peers (send $\leftrightarrow$ receive)
identification.
\item Then as the first step in the analysis phase, this instrumented program is executed using the test suites and program traces are collected.
\item Forward flow analysis is done on the collected traces
\item Using the results of the previous step, variables contributing to distributed state is identified.
\item From the dumped variable values at annotated program points (after multiple executions), only the values of variables chosen in the previous step are selected.
\item Selected variable values belonging to 2 distinct annotated program points in the 2 nodes are fed to Daikon for inferring invariants.
\end{itemize}

@@

\section{Timeline}
